<<<<<<< HEAD
---
title: "Fig1-S1_causal-model"
author: "Mitchell Muniak"
date: "5/23/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(igraph)

```


This is figure 1 for the paper.  More edits will be made in adobe illustrator.


```{r, out.width="100%", out.height="100%"}


g <- graph.formula("CCI" -+ "ATB" -+ "Microbiome" -+ "T-cell Mediated Inflammation" -+                                "ICI Response" -+ "Overall Survival",
                   "CCI" -+ "Corticosteroids" -+ "Prostaglandin Inflammation" -+ "Microbiome" -+                       "T-cell Mediated Inflammation",
                   "CCI" -+ "PPI" -+ "Microbiome",
                   "CCI" -+ "H2B" -+ "Microbiome",
                   "CCI" -+ "NSAIDs" -+ "Prostaglandin Inflammation",
                   "Corticosteroids" -+ "T-cell Mediated Inflammation",
                   "Age" -+ "Prostaglandin Inflammation" -+ "T-cell Mediated Inflammation",
                   "Age" -+ "T-cell Mediated Inflammation",
                   "Staging" -+ "Prostaglandin Inflammation",
                   "Age" -+ "ECOG" -+ "Prostaglandin Inflammation",
                   "CCI" -+ "ECOG" -+ "BMI" -+ "Prostaglandin Inflammation",
                   "ECOG" -+ "T-cell Mediated Inflammation",
                   simplify = TRUE
                   )
V(g)$color <- c("#cfb4de", "#77d1e5", "#aadab4", "#aadab4", "#e2bf99", "#e2bf99", "#77d1e5", "#aadab4", "#77d1e5", "#77d1e5", "#77d1e5","#cfb4de","#cfb4de","#cfb4de","#cfb4de")
edge.widths <- c(1,1,1,1,1,1,5,5,5,5,1,5,1,5,1,1,1,1,1,1,1,1,1,1,1)


plot.igraph(g, vertex.label.color="black", vertex.size=20, edge.arrow.size=0.5, edge.arrow.width=0.5, edge.width = edge.widths)
```
This is figS1 for the paper.

```{r}
E(g)$label = letters[1:ecount(g)]
plot(g)
layout.circle(g)
tkplot(g, vertex.label.color="black", vertex.size=20, edge.arrow.size=0.5, edge.arrow.width=0.5, edge.width = edge.widths, edge.label.color="black", layout=layout.circle, size=300)


```

=======
---
title: "Fig1-S1_causal-model"
author: "Mitchell Muniak, Daniel Spakowicz"
date: "5/23/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(igraph)
```


This is figure 1 for the paper.  More edits will be made in adobe illustrator.


```{r, out.width="100%", out.height="100%"}

g <- graph.formula("CCI" -+ "ATB" -+ "Microbiome" -+ 
                     "T-cell Mediated Inflammation" -+ "ICI Response" -+ 
                     "Overall Survival",
                   "CCI" -+ "Corticosteroids" -+ "Prostaglandin Inflammation" -+ 
                     "T-cell Mediated Inflammation",
                   "CCI" -+ "NSAIDs" -+ "Prostaglandin Inflammation" -+ "Microbiome",
                   "CCI" -+ "PPI" -+ "Microbiome",
                   "CCI" -+ "H2B" -+ "Microbiome",
                   "Corticosteroids" -+ "T-cell Mediated Inflammation",
                   "Age" -+ "Prostaglandin Inflammation",
                   "Age" -+ "T-cell Mediated Inflammation",
                   "Age" -+ "Microbiome",
                   "Staging" -+ "Prostaglandin Inflammation",
                   "CCI" -+ "ECOG" -+ "Prostaglandin Inflammation",
                   "ECOG" -+ "T-cell Mediated Inflammation",
                   "ECOG" -+ "BMI" -+ "Prostaglandin Inflammation",
                   "BMI" -+ "T-cell Mediated Inflammation",
                   "BMI" -+ "Microbiome",
                   simplify = TRUE
                   )

# Set colors by categories -- medications, clinical variables, mediators of 
# response and outcomes
V(g)$color <- c("#81d5dd", "#b8d8a7", "#b8d8a7", "#e5bb99", "#e5bb99", 
                "#81d5dd", "#b8d8a7", "#81d5dd", "#81d5dd", "#81d5dd", 
                "#cfb4de","#cfb4de","#cfb4de","#cfb4de","#cfb4de")

# Add edge labels for citing references
edge_attr(g) <- list(name = letters[1:length(E(g)])

# Create figure Supplemental-1
plot.igraph(g, 
            vertex.label.color = "black", 
            vertex.size = 20, 
            edge.arrow.size = 0.5, 
            edge.arrow.width = 0.5,
            edge.label)

```

```{r}
# Modify edge widths to define our hypothesized primary pathway
sizes <- ends(g, E(g))
sizes$edge.widths <- c(1,1,1,1,1,1,1,1,7,7,1,1,1,1,1,1,1,1,1,7)
sizes$arrow.sizes <- c(1,1,1,1,1,1,1,1,7,7,1,1,1,1,1,1,1,1,1,7)

# Create Figure 1, to be manipulated in Adobe Illustrator
tkplot(g, vertex.label.color = "black", 
       vertex.size = 20, 
       edge.width = sizes$edge.widths,
       edge.arrow.size = sizes$arrow.sizes, 
       edge.arrow.width = sizes$.arrow.sizes)
```
>>>>>>> ff3433cf331ea77b2945539edce0f34afd33476b
