---
title: "Untitled"
author: "Rebecca Hoyd"
date: "April 10, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(ggtree)
library(phylogram)
library(rotl)
library(dplyr)
library(forcats)
library(gridExtra)
library(tidyr)
```

# Getting information from the OTL (open tree of life) on the interesting taxa and creating initial dendrogram

```{r access data from otl}
hazardtable <- readRDS("hazard-table.RDS")
antiorder <- hazardtable %>%
  arrange(Average.Rank) 
antiorder <- antiorder$Antibacterial

litmics <- c("akkermansia muciniphila",
                                   "parabacteroides distasonis",
                                   "bacteroides nordii",
                                   "bacteroides clarus",
                                   "clostridium bolteae",
                                   "cloacibacilis porcorum",
                                   "ruminococcus bromii",
                                   "porphyromonas pasteri",
                                   "clostridium hungatei",
                                   "gardnerella vaginalis",
                                   "prevotella histicola",
                                   "desulfovibrio alaskensis",
                                   "collinsella aerofaciens",
                                   "bifidobacterium adolescentis",
                                   "klebsiella pneumoniae",
                                   "bifidobacterium longum",
                                   "blautia obeum",
                                   "roseburia intestinalis")

taxa <- tnrs_match_names(names = litmics)

tree <- tol_induced_subtree(ott_ids = ott_id(taxa))

tree$tip.label <- gsub("_ott\\d+", "", tree$tip.label)
tree$tip.label <- gsub("_", " ", tree$tip.label)

d <- fortify(tree)
d <- subset(d, isTip)
order <- with(d, label[order(y, decreasing=T)])

tree$tip.label[1] <- "Klebsiella pneumoniae"
```


# Adding info on responders/non-responders

```{r create frame of info for aesthetics}
resp.stat <- c("r", "n", "n", "n", "n", "r", "r", "r", "r", "n", "n", "n", "r", "r", "r", "r", "n", "n")

resp.ref <- c("r", "r", "r", "r", "r", "r", "g", "g", "g", "g", "g", "g", "m", "m", "m", "m", "m", "m")
resp.key <- as.data.frame(cbind(search_string = litmics, resp.stat, resp.ref)) %>%
  mutate(fixed = "hold") 

resp.key <- taxa %>%
  dplyr::select(search_string, unique_name) %>%
  left_join(resp.key) %>%
  mutate(tip.label = unique_name) %>%
  dplyr::select(tip.label, resp.stat, resp.ref)


resp.key$tip.label <- gsub("_ott\\d+", "", resp.key$tip.label)
resp.key$tip.label <- gsub("_", " ", resp.key$tip.label)
resp.key$tip.label[15] <- "Klebsiella pneumoniae"
```

```{r create dendrogram}
tree.plot <- ggtree(tree)  %<+%
  resp.key + 
  geom_tiplab(aes(color = resp.stat), geom = "text", offset = 0.2) +
  #geom_text2(aes(subset=!isTip, label=node), hjust=-.3) +
  #geom_nodelab() +
  scale_color_manual(breaks = c("n", "r"), values = c("darkred", "royalblue")) +
  geom_tippoint(aes(shape = resp.ref), size = 5) +
  scale_shape_manual(breaks = c("g", "m", "r"), values = c("square", "circle", "triangle")) +
  geom_cladelabel(node = 30, label = "Bacteroidetes \n(Gopalakrishnan)", geom = "text", color = "darkred", offset = -2.3, offset.text = -2.7, align = TRUE) +
  geom_cladelabel(node = 22, label = "Firmicutes \n(Gopalakrishnan)", geom = "text", color = "royalblue", offset = -4.3, offset.text = -2.6, align = TRUE) +
  xlim(c(0,11.5)) 
  
tree.plot
```


# Accompanying susceptibility heatmap
```{r define data for heatmap}
m <- "m"
n <- "n"
y <- "y"

ceph <- c(n,n,n,n,n,y,y,y,y,y,y,n,n,n,n,n,y,n)
pip <- c(y,y,y,y,y,y,y,y,y,y,y,y,y,y,y,y,y,n)
amclac <- c(y,y,y,y,y,y,n,y,y,y,y,y,y,y,y,y,y,y)
clin <- c(y,y,y,y,y,y,n,y,y,y,y,n,n,n,n,n,y,y)
fq <- c(y,y,y,y,y,n,y,y,y,y,y,y,y,y,y,y,y,y)
macr <- c(y,y,y,y,y,y,n,y,y,y,y,n,n,n,n,n,y,y)
metr <- c(y,y,y,y,y,n,y,n,n,n,n,y,y,y,y,y,y,n)
trim <- c(n,n,n,n,n,n,n,n,n,n,n,n,n,n,n,n,n,y)
van <- c(n,n,n,n,n,n,y,y,y,y,y,y,y,y,y,y,n,n)
tetr <- c(y,y,y,y,y,y,n,y,y,y,y,y,y,y,y,y,y,y)
line <- c(y,y,y,y,y,y,y,y,y,y,y,y,y,y,y,y,y,n)

susc <- as.data.frame(cbind(taxon = order, Cephalosporins = ceph, Piperacillin = pip, Amoxicillin = amclac,  Clindamycin = clin, Fluoroquinolone = fq, Macrolide = macr, Metronidazole = macr, Sulfamethoxazole = trim, Vancomycin = van, Tetracycline = tetr, Linezolid = line))

susc <- susc %>%
  gather(-taxon, key = "Antibiotic", value = Effective)
```

```{r construct heatmap}
heat <- ggplot(data = susc, aes(fct_relevel(taxon, rev(order)), fct_relevel(Antibiotic, c("Cephalosporins", "Piperacillin", "Amoxicillin", antiorder[-1])))) + 
  geom_tile(aes(fill = Effective, color = "black")) +
  scale_fill_manual(breaks = c("yes", "no"), values = c("lightcyan1", "seagreen")) +
  scale_color_manual(breaks = "black", values = "grey85") +
  coord_flip() +
  labs(x = "", y = "") +
  scale_y_discrete(breaks = c("Cephalosporins", "Piperacillin", "Amoxicillin", "Clindamycin", "Vancomycin", "Sulfamethoxazole", "Tetracycline", "Fluoroquinolone", "Macrolide", "Metronidazole", "Linezolid"), labels = c("Cephalosporins", "Piperacillin-Tazobactam", "Amoxicillin-Clavulanate", "Clindamycin", "Vancomycin", "Sulfamethoxazole-Trimethoprim", "Tetracycline", "Fluoroquinolone", "Macrolide", "Metronidazole", "Linezolid")) +
  theme_bw() +
  theme(axis.text.x = element_text(hjust = 1, angle = 45, size = 10), axis.text.y = element_blank(), axis.ticks.y = element_blank(), legend.position = "none")

heat
```

# Arrange and save the results

```{r}

test2 <- grid.arrange(
  grobs = list(tree.plot, heat),
   widths = c(2,1.2),
   heights = c(0, 1, .23),
   layout_matrix = rbind(c(NA,2),
                         c(1,2),
                         c(NA,2))
) 


# ggsave(plot = test2, filename = "../figures/Figure-4/abx_susceptibility_dendrogram.png", device = "png", height = 8, width = 9)

```

# Fisher's exact tests

Counting
```{r}
test <- susc %>%
  mutate(tip.label = ifelse(taxon == "Klebsiella pneumoniae (species in domain Eukaryota)", "Klebsiella pneumoniae", as.character(taxon))) %>%
  left_join(resp.key)

test2 <- test %>%
  group_by(Antibiotic, Effective, resp.stat) %>%
  tally() %>%
  arrange(Antibiotic, Effective, resp.stat)
```

Ammoxicillin-Clavulanate
```{r}
x <- c(1,0,8,9)
y <- matrix(x, ncol = 2)
fisher.test(y)
```

Cephalosporin
```{r}
x <- c(7,4,2,5)
y <- matrix(x, ncol = 2)
fisher.test(y)
```

Fluoroquinolone
```{r}
x <- c(0,1,9,8)
y <- matrix(x, ncol = 2)
fisher.test(y)
```


Linezolid
```{r}
x <- c(0,1,9,8)
y <- matrix(x, ncol = 2)
fisher.test(y)
```

Macrolide
```{r}
x <- c(4,2,5,7)
y <- matrix(x, ncol = 2)
fisher.test(y)
```

Metronidazole
```{r}
x <- c(4,2,5,7)
y <- matrix(x, ncol = 2)
fisher.test(y)
```

Piperacillin-Tazobactam
```{r}
x <- c(0,1,9,8)
y <- matrix(x, ncol = 2)
fisher.test(y)
```

Sulfamethoxazole-Trimethoprim
```{r}
x <- c(9,8,0,1)
y <- matrix(x, ncol = 2)
fisher.test(y)
```

Tetracycline
```{r}
x <- c(1,0,8,9)
y <- matrix(x, ncol = 2)
fisher.test(y)
```

Vancomycin
```{r}
x <- c(4,4,5,5)
y <- matrix(x, ncol = 2)
fisher.test(y)
```


